---
title: "Web Scraping for Sports Data"
author: Wanwan Xu
date: October 5, 2019
output:
  revealjs::revealjs_presentation:
    theme: simple
    highlight: pygments
    center: false
---

```{r setup, echo = FALSE}
options(width = 90)
```

## Outline

- What is web scraping and why do we need it

- Types of web scraping

- Using R

- Case study (college basketball)

- Summary


## Getting Started

- Prerequisites: R and RStudio preinstalled.

- A list of R packages needed is given below.

```{r pckgs, eval=FALSE, message=FALSE, warning=FALSE}
install.packages("rvest",repos = "http://cran.us.r-project.org")
install.packages("RSelenium",repos = "http://cran.us.r-project.org")
library(devtools)
install_github("skoval/deuce")
```

- Use `help()` function to take a closer look.

```{r help, eval = FALSE}
?help                         # details on using the `help` function
help(package = "deuce")       # information about the stats package
```


## Motivation?

> - Have a topic in mind, but not sure Where to find the data. 

> - Found related data online, not able to download directly.

> - Need a reproducible way to capture similar data repeatedly.

> - 
